---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

library(tidyverse)
csv_url <- "https://docs.google.com/spreadsheets/d/e/2PACX-1vSTqLztmVx6yPNjSc9U15Mf7l1Gf6RCFr_NoYW49GvEhBULljUHnVZwvjuIsMYDkTDnoQ6VVrX6iFOc/pub?output=csv"

logged_data <- read_csv(csv_url)

names(logged_data)

latest_data <- logged_data %>%
  rename(
    timestamp = Timestamp,
   Yes_or_No = `Did you play computer games today?`,
    videogame_hours = `How much time do you spend playing games (hours)?`,
    game_type = `What game did you play today?`,
  )

top_YesNo <- latest_data %>%
  count(Yes_or_No, sort = TRUE) %>%
  slice(1) %>%
  pull(Yes_or_No)

mean_hours <- latest_data %>%
  summarise(mean_hours = mean(videogame_hours), na.rm = TRUE) %>%
  pull(mean_hours)

top_game <- latest_data %>%
  count(game_type, sort = TRUE) %>%
  slice(1) %>%
  pull(game_type)


```

```{css}
body {
  background-color: #00045E;
  font-family: Arial, sans-serif;
  color: #DEF3FA;
  padding: 35px;
}

h2 {
  color: #CFE8FF;
  border-bottom: 2px solid #CFE8FF;
  padding-bottom: 2px;
  font-size: 40px;
}

p {
  font-size: 16px;
  line-height: 1.6;
}

img {
  border-radius: 10px;
}

```

## Video game habit observation logging report
I have summarized the data collected from my survey into a report interpreting gaming patters, habits and preferences.

According to my survey, the most of my respondents said **`r top_YesNo`** to playing games in a day.

Where they spend an average of **`r round(mean_hours, 2)` hours** on gaming a day.

```{r}
ggplot(latest_data, aes(x = Yes_or_No)) +
  geom_bar(aes(fill = Yes_or_No)) +
  labs(
    title = "Did people play games that day",
    x = "Yes or No",
    y = "Count"
  ) +
  scale_fill_manual(values = c("Yes" = "#00C40D", "No" = "#FA2D2D")) +
  theme_minimal() +
theme(
    plot.title = element_text(size = 20)
  )
```



With the most common/top played game being **`r top_game`** as shown below.

```{r}
ggplot(latest_data, aes(x = game_type)) +
  geom_bar(fill = "#7600C4") +
  labs(
    title = "Most Common Game played",
    x = "game type",
    y = "Count"
  ) +
  theme_minimal() +
theme(
    plot.title = element_text(size = 20)
  )
```


